\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

% CUSTOM COMMANDS
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeEduheading}[4]{
  \item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    \hspace*{0.5em}\textbf{\small#3} & {\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\small\:\textbf{#1}} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{ 
    \item
    \textbf{\small #1} -- \textbf{\small #2}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{ 
 \item
    \begin{tabular*}{\textwidth}{@{}l p{\dimexpr\textwidth-1.5cm}@{}}{\small\textbf{#1}}\hspace{0.5em} & {\small #2} \\ 
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%%%%%%  DOCUMENT STARTS HERE  %%%%%%
\begin{document}

%---------------HEADER---------------
\begin{center}
    {\Huge \scshape Tyler O'Neil} \\
    \vspace{4pt}
    \small \faIcon{canadian-maple-leaf} Toronto, Ontario ~
    \href{mailto:tyleroneildev@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tyleroneildev@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/tyler-oneil-dev/}{\raisebox{-0.1\height}\faLinkedin\ \underline{LinkedIn}} ~ 
    \href{https://github.com/tyleroneil72}{\raisebox{-0.1\height}\faGithub\ \underline{GitHub}} ~
    \href{https://tyleroneil.dev}{\raisebox{-0.2\height}\faGlobe\ \underline{tyleroneil.dev}}
    \vspace{-6pt}
\end{center}

%---------------EXPERIENCE---------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading{Exchange Solutions Inc.}{Toronto, Ontario}
      \resumeSubSubheading{Software Developer}{May 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Develop scalable features for a large-scale loyalty platform, contributing across frontend {\bf(React, TypeScript)} and backend {\bf(AWS serverless microservices, TypeScript)} development in a production environment.}
        \resumeItem{Ensure code quality and reliability by writing and maintaining {\bf unit tests} and participating in peer code reviews.}
        \resumeItem{Apply {\bf agile} methodologies to drive new feature development, optimize system performance, and ensure code maintainability.}
        \resumeItem{Work closely with senior engineers and product owners, further deepening technical expertise and product knowledge to deliver solutions impacting millions of end users.}
      \resumeItemListEnd

    \resumeSubSubheading{Software Developer Intern}{May 2024 -- August 2024}
      \resumeItemListStart
        \resumeItem{Contributed to both frontend {\bf(React, TypeScript)} and backend {\bf(AWS serverless microservices, TypeScript)} development on a large-scale, production-grade loyalty platform.}
        \resumeItem{Developed practical skills in {\bf cloud infrastructure (AWS)}, {\bf CI/CD (Jenkins)}, and Atlassian tools in a collaborative, fast-paced environment.}
      \resumeItemListEnd

      \resumeSubSubheading{Software Developer Intern (Innovation Labs)}{May 2023 -- September 2023}
      \resumeItemListStart
        \resumeItem{Developed proof-of-concept {\bf Retrieval Augmented Generation (RAG)} AI agents using {\bf Node.js} and {\bf OpenAI APIs}, in direct collaboration with the Director of Innovation Labs.}
        \resumeItem{Conducted {\bf research and rapid prototyping} that directly contributed to the adoption of {\bf generative AI} capabilities in the company's core loyalty product.}
      \resumeItemListEnd

    \resumeSubheading{PresenTEC Solutions}{Vaughan, Ontario}
      \resumeSubSubheading{Front-End Developer Intern}{December 2022 -- April 2023}
      \resumeItemListStart
        \resumeItem{Maintained and improved company website functionality using {\bf WordPress} and custom development.}
        \resumeItem{Implemented UI improvements following company brand guidelines to ensure consistent user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%---------------PROJECTS---------------
\section{Projects \footnotesize -- More information available on my {\href{https://tyleroneil.dev}{Website~\faExternalLink*}}}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {{Nest}}
      {Typescript, Next.js, NextAuth.js, PostgreSQL, Prisma, Tailwind CSS, Stripe} 
    \resumeItemListStart
      \resumeItem{Designed and developed a minimalist investment tracker that provides users with personalized insights and projections for their portfolios, supporting multiple accounts and asset types.}
      \resumeItem{Implemented secure {\bf Google sign-in}, account management, and authorization features to protect user privacy and ensure data integrity.}
      \resumeItem{Integrated subscription billing ({\bf Stripe}) and direct brokerage connections ({\bf SnapTrade}), enabling users to track investments manually or automatically with real-time data.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://duordle.net}{Duordle~\faExternalLink*}}
      {Typescript, React.js, Node.js, Express.js, MongoDB, Tailwind CSS, Docker, Jest} 
    \resumeItemListStart
      \resumeItem{Developed a multiplayer online word game where users collaboratively guess words, utilizing {\bf Socket.io} for real-time communication between players.}
      \resumeItem{Containerized the application with {\bf Docker} to enable streamlined deployment and seamless scalability.}
      \resumeItem{Implemented comprehensive unit testing using {\bf Jest} to ensure code reliability and robustness throughout development.}
      \resumeItem{Set up a {\bf CI/CD} pipeline and utilized {\bf Git} for version control, streamlining the development workflow and enabling efficient project management while working independently.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%---------------EDUCATION---------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEduheading
      {McMaster University}{Hamilton, Ontario}
      {Bachelor of Technology, Software Engineering Technology}{}
      \item \hspace*{0.5em}{\footnotesize Pursuing part-time while working full-time as a developer \textbar\ VP of Projects, McMaster Open Source Society (MOSS)}
  \resumeSubHeadingListEnd

%---------------TECHNICAL SKILLS---------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages:}
      {Javascript/Typescript, Python, Java, C\#, Bash, SQL, HTML, CSS}
    \resumeSubItem{Technologies/Frameworks:}
      {Node.js, Express.js, React.js, Next.js, Tailwind CSS, Bootstrap, Jest, .NET, Spring Boot}
    \resumeSubItem{Databases:}
      {MySQL, PostgreSQL, Oracle SQL, SQLite, Snowflake, MongoDB}
    \resumeSubItem{Development Tools:}
      {AWS, Docker, Linux, Git, GitHub, Jenkins, Postman, Stripe, Jira, Bitbucket, Confluence}
  \resumeSubHeadingListEnd

\end{document}